---
title: "Automotives Example"
bibliography: ../references.bib
---

In this example, I apply the matrix to the automotive industry

# Set up Coding Environment

```{r}
#| label: setup
#| include: false
#| code-fold: true

# Install reticulate if not already installed
if (!require("reticulate", quietly = TRUE)) {
    install.packages("reticulate")
}

library(reticulate)

# Set Python environment to natcapenv
use_condaenv("natcapenv", required = TRUE)
```

# Find and Geocode Factories 

Naively, we know from Bloomberg a list of publicly traded automotive companies. Use the `geocode_factories.py` script to search the internet for factory information and geocode them using openstreet maps. 

Once this has been figure out, proceed with the following companies and tickers: 

* 7203 JP	TOYOTA MOTOR
* 1211 HK	BYD COMPANY
* GM US	GENERAL MOTORS C
* 005380 KS	HYUNDAI MOTOR
* MBG GR	MERCEDES-BENZ GR
* BMW GR	BMW AG
* VOW GR	VOLKSWAGEN AG
* RACE US	FERRARI NV
* 7267 JP 	HONDA MOTOR CO
* MSIL IN 	MARUTI SUZUKI IN
* MM IN 	MAHINDRA & MAHIN
* P911 GY 	DR ING HC F PORS
* 000270 KS 	KIA CORP
* BJAUT IN 	BAJAJ AUTO LTD
* STLAM IM 	STELLANTIS NV
* SERES GROUP CO-A	SERES GROUP CO-A
* 7269 JP 	SUZUKI MOTOR
* 600104 CH 	SAIC MOTOR-A
* 2333 HK 	GWMOTOR
* GELYF US 	GEELY AUTOMOBILE
* EIM IN 	EICHER MOTORS
* HYUNDAI IN 	HYUNDAI MOTOR IN
* TVSL IN 	TVS MOTOR CO LTD
* RIVN US 	RIVIAN AUTOMOT-A
* LI US Equity	LI AUTO INC -ADR
* 9868 HK Equity	XPENG INC-A SHRS
* 7270 JP Equity	SUBARU CORP
* 000625 CH Equity	CHONGQING CHAN-B
* TMPV IN Equity	TATA MOTORS PASS
* P911 GY Equity	PORSCHE AUTO-PRF
* HMCL IN Equity	HERO MOTOCORP LT
* NIO US Equity	NIO INC - ADR
* RNO FP Equity	RENAULT SA
* VOLCARB SS Equity	VOLVO CAR AB-B
* 601238 CH Equity	GUANGZHOU AUTO-H
* 489 HK Equity	DONGFENG MOTOR-H
* FROTO TI Equity	FORD OTO
* 7201 JP Equity	NISSAN MOTOR CO
* 7272 JP Equity	YAMAHA MOTOR CO
* 9863 HK Equity	ZHEJIANG LEAPM-H
* 601777 CH Equity	CHONGQING AFAR-A
* 600733 CH Equity	BAIC BLUEPARK-A
* 603129 CH Equity	ZHEJIANG CFMOT-A
* 7261 JP Equity	MAZDA MOTOR
* 603766 CH Equity	LONCIN MOTOR C-A
* 1585 HK Equity	YADEA GROUP HOLD
* TOASO TI Equity	TOFAS
* 7211 JP Equity	MITSUBISHI MOTOR
* LCID US Equity	LUCID GROUP INC
* 301345 CH Equity	ZHEJIANG TAOTA-A
* FML IN Equity	FORCE MOTORS LTD
* 1114 HK Equity	BRILLIANCE CHINA
* GTCAP PM Equity	GT CAPITAL HOLD
* 600418 CH Equity	ANHUI AUTOMOBI-A
* HOG US Equity	HARLEY-DAVIDSON
* 600006 CH Equity	DONGFENG AUTO-A
* 1958 HK Equity	BAIC MOTOR-H
* MHSC IN Equity	MAHARASHTRA SC
* 2206 TT Equity	SANYANG MOTOR
* PSNY US Equity	POLESTAR A-A ADS
* HLI MK Equity	HONG LEONG INDS
* OTKAR TI Equity	OTOKAR
* 2201 TT Equity	YULON MOTOR
* 2204 TT Equity	CHINA MOTOR
* 7222 JP Equity	NISSAN SHATAI
* AML LN Equity	ASTON MARTIN
* LOT US Equity	LOTUS TECHNOLOGY
* ATLH PA Equity	ATLAS HONDA
* PIA IM Equity	PIAGGIO & C. SPA
* GBCO EY Equity	GB CORP
* JYGCLZ CH Equity	JIANGSU YUEDA -A
* BJAUT IN Equity	BAJAJ MOBILITY A
* 003620 KS Equity	KG MOBILITY CO
* DRB MK Equity	DRB-HICOM BHD
* 2227 TT Equity	YULON NISSAN
* LVWR US Equity	LIVEWIRE GROUP I
* 8937 TT Equity	HER CHEE
* 1656311D CH Equity	NIU TECHNOLO-ADR
* 3333 HK Equity	CHINA EVERGRANDE
* IMS IM Equity	IMMSI SPA
* HCAR PA Equity	HONDA ATLAS CAR
* 0K4R LN Equity	CARS MOTORCYCLES
* NRDE US Equity	NU RIDE INC



```{python}
#| label: webscrap-factory-locations
#| code-fold: true

# Set location to save geocodes
import os
import sys

# Add scripts directory to path so we can import geocode_factories
sys.path.insert(0, "E:/matrix/thematrix/scripts")
from geocode_factories import search_factories, geocode_from_csv

# Set directory for firm geocodes
output_dir = "E:/matrix/data/firms/geocodes"
os.makedirs(output_dir, exist_ok=True)

# Define output files
ford_output_1 = os.path.join(output_dir, "F_factory_geocodes.csv")
ford_output_2 = os.path.join(output_dir, "F_factory_info.csv")
tesla_output_1 = os.path.join(output_dir, "TSLA_factory_geocodes.csv")
tesla_output_2 = os.path.join(output_dir, "TSLA_factory_info.csv")

# Search Ford factories 
if not os.path.exists(ford_output_2):
    print("Geocoding Ford factories (Step 1: Search)...")
    search_factories("F US", "Ford Motor", ford_output_1)
    print("Geocoding Ford factories (Step 2: Detailed geocoding)...")
    geocode_from_csv("F US", ford_output_1, ford_output_2)
else:   
    print(f"Ford geocodes already exist at {ford_output_2}")

# Search Tesla factories 
if not os.path.exists(tesla_output_2):
    print("\nGeocoding Tesla factories (Step 1: Search)...")
    search_factories("TSLA US", "Tesla", tesla_output_1)
    print("Geocoding Tesla factories (Step 2: Detailed geocoding)...")
    geocode_from_csv("TSLA US", tesla_output_1, tesla_output_2)
else:
    print(f"Tesla geocodes already exist at {tesla_output_2}")

print("\nDone!")
```


# Create a Map of Industry 

Use the geocodes to create an interactive map of the factories and production locations for the industry in question. 


```{r}
#| label: factory-dataset
#| cache: true
#| code-fold: true

library(tidyverse)
library(rio)
setwd("E:/matrix/")

ford_factories <- import("./data/firms/F_factory_info.csv")
tesla_factories <- import("./data/firms/geocodes/TSLA_factory_geocodes.csv")

# factories <- rbind(ford_factories, tesla_factories)

```

```{r}
#| label: factory-map
#| cache: true
#| code-fold: true
#| fig-cap: "Global distribution of manufacturing facilities"

library(leaflet)

company_icons <- iconList(
    "F US" = makeIcon(
        iconUrl = "https://upload.wikimedia.org/wikipedia/commons/3/3e/Ford_logo_flat.svg",
        iconWidth = 30,
        iconHeight = 30
    )
)

leaflet(ford_factories) %>%
    addTiles() %>%
    addMarkers(
        ~longitude,
        ~latitude,
        icon = ~ company_icons[ticker],
        label = ~ paste0(facility_name, " (", ticker, ")"),
        popup = ~ paste(
            "<b>", facility_name, "</b><br>",
            "Ticker: ", ticker, "<br>",
            "Type: ", facility_type, "<br>",
            "Products: ", products, "<br>",
            "Active: ", status
        )
    )

```


TODO: Add a version with bi-variate map of emissions and ecosystem services as a layer. 